Probability

### 2016-04-25 prob.tex
prob.tex \section{Quantum Probability Spaces} updated...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}

@@

We now formalize a \emph{quantum probability space} as follows~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}.
We first assume an ambient Hilbert space~$\Hilb$ and define the
set of events $\qevents$ as all \emph{projections} on~$\Hilb$.
Each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows\footnote{Recently, people extend the domain of $\mu_{\psi}$ to all operators~$\mathcal{A}$
on $\Hilb$ and consider $\mu_{\psi}:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu_{\psi}\left(A\right)$
is the expectation value of $A$. We does not take this approach because
we want to focus only on probability. }: 
\begin{equation}
\mu_{\psi}(E)= \ip{\psi}{E\psi} \label{eq:Born}
\end{equation}
which is called the Born rule~\cite{Born1984,Mermin2007}.\\
\yutsung{One small thing is whether we should say
\begin{quote}
for each normalized state~$\ket{\psi}$...$\mu_{\psi}(E)=\ip{\psi}{E\psi}$
\end{quote}
as in Mermin~\cite{Mermin2007} and Maassen~\cite{Maassen2010}
or
\begin{quote}
for each state~$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $...$\mu_{\psi}(E)=\frac{\ip{\psi}{E\psi}}{\ip{\psi}{\psi}}$
\end{quote}
as in Abramsky~\cite{DBLP:journals/corr/abs-0910-2393}. Personally,
I prefer Abramsky's approach, because normalizing a state in DQT is
messier than in CQT, and we have already considered states whose norm
is not one in our previous paper~\cite{DQT2014}.}\\
These two conditions define quantum probability measures. Recall that
the Born rule (\ref{eq:Born}) induces a probability measure from
a state. Naturally, we may ask: is every probability measure induced
from a state by the Born rule? The answer is yes by Gleason's theorem
when the dimension~$\ge3$ and extend the domain of the Born rule
to mixed state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}

@@

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu_{0}$, our $\mu_{0}$ is actually
given by a simple formula~$\melement{0}{E}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\mu_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
Naturally, we may ask: is every probability measure induced from a
state by the Born rule? The answer is yes by Gleason's theorem when
the dimension~$\ge3$ and extend the domain of the Born rule to mixed
state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
